Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-05-25 edubots_surveys.Rnw
Add methodology section explaining how surveys were made refs #20

% Maybe move it to a different place later
In the present work we aim to complement this study with teachers, who are the ones that actually would need to implement, configure and maybe program chatbots. Thus, we have performed a survey among 300 teachers asking about their attitudes towards the use of bots or chatbots in their classes. We analyse their responses, since we are interested in discussing implications and the impact for the development of future technology-enhanced tools and the Education institutions policies regarding the following research questions:
\begin{itemize}
\item{ RQ1 - Are teachers already using messaging apps in their classes? } %This was the second survey, not the  first survey. I wonder if maybe we could invert the presentation order - JJ
\item{ RQ2 - Which kind of chatbots would teachers find useful in their classes?? }
\item{ RQ3 - Which kind of interaction do teachers prefer with their students? }

@@

>>>>

% Maybe move it to a different place later
In the present work we aim to complement the aforementioned study with teacher attitudes; teachers are the ones that actually would need to implement, configure and maybe program chatbots. Thus, we have performed a survey among 300 teachers asking about their attitudes towards the use of bots or chatbots in their classes. We analyse their responses, since we are interested in discussing implications and the impact for the development of future technology-enhanced tools and the Education institutions policies regarding the following research questions:
\begin{itemize}
\item{ RQ1 - Are teachers already using messaging apps in their classes? } %This was the second survey, not the  first survey. I wonder if maybe we could invert the presentation order - JJ
\item{ RQ2 - Which kind of chatbots would teachers find useful in their classes?? }
\item{ RQ3 - Which kind of interaction do teachers prefer with their students? }

@@

\section{Methodology}

Our intention from the beginning was to try and gather a sufficient amount of responses in all sectors, as well as cover different sectors of higher education. This is why we created a Google Form, in Spanish, which was intended to be answered in a very short amount of time. Initially, our intention was to mirror the questions used in \cite{MoraChatbos2021}; however, an initial exploration of results led us to create a second survey.
% Questions should probably be included here.

The initial survey was done in two different forms, one for university and other for tertiary non-university teachers. Questions and responses were the same, except for the type of tertiary degrees that were taught. We got around 300 responses to this one, with two thirds of them coming from university teachers, the rest from high school teachers. In both cases, we used mainly mailing lists, as well as Telegram groups, to spread the link to the form. The university form was spread in Spanish (mainly Andalucía and Galicia) universities, as well as Costa Rica and Mexico. The tertiary non-university teachers are mainly in Andalucía. Dissemination and answers took place in the first quarter of 2021, post-pandemic and while, at least in Spain, many universities had mandatory virtual teaching.

The second survey followed the same paths, only in this case there was a single questionnaire. It was filled by teachers that were also students in a teacher formation course (on the use of new technologies in higher education, around 1/4 of them) as well as University of Granada teachers to knew about it by emails from the authors, as well as from the vicedeanship for International Relations that included it in its newsletter. This means that there might be a higher proportion of 1) teachers with few years of experience 2) teachers from the computer science faculty and 3) teachers from Granada. We think, however that there's no explicit bias in this selection, although of course specific percentages will vary.
